Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-08-17 Masterarbeit_Robotik_Pamuk.tex
clearpage
Problem and Task Definition

\section{Problem and Task Definition}

\section{Objective}

>>>>

\clearpage
\section{Problem and Task Definition}
As stated previously, virtualization of real-time systems has many advantages in comparison to traditional hardware-based approaches. Solutions based on pure hardware are often built for a distinct purpose and are hence limited in flexibility. It is difficult to adapt the hardware topology to new requirements or new applications. Moreover, during periods when the demand is lower, expensive hardware may sit idle, leading to inefficient use of resources and a poor return on investment. Another crucial factor is of course the high cost factor associated with procuring and maintaining separate hardware for each real-time system. Especially when organizations scale their operations, they have to add more physical machines, and the expenses rise rapidly. Besides, one needs physical access to the hardware for any updates or maintenance, which is hard to achieve, especially for systems in remote or difficult-to-access locations. This can lead to system downtime and may not only disrupt the operations but can also result in lost productivity and potential revenue.

Virtualization promises overcoming these challenges

\begin{comment}
1. Flexibility and Resource Utilization

Virtualization allows for more efficient use of hardware resources by enabling multiple real-time systems to run on a single physical machine. This improved resource utilization can lead to significant cost savings and increased flexibility in system design.

Evidence: A study by Cucinotta et al. (2018) demonstrated that virtualization techniques could effectively support real-time applications while maintaining their timing constraints. They showed that proper scheduling and resource allocation in virtualized environments could provide performance comparable to bare-metal systems.

2. Isolation and Security

Virtualization provides isolation between different real-time systems, enhancing security and reliability. Each virtualized system can operate independently, reducing the risk of interference or security breaches between applications.

Evidence: Research by Lackorzynski et al. (2017) proposed a virtualization architecture for mixed-criticality systems, showing how virtualization can effectively isolate different security levels and criticality domains in real-time systems.

3. Scalability

Virtualized real-time systems can be more easily scaled up or down based on demand, allowing for more efficient resource allocation and improved system responsiveness.

Evidence: A paper by Oliveira et al. (2019) presented a scalable virtualization solution for real-time systems in cloud environments, demonstrating how virtualization can enable dynamic resource allocation for real-time tasks.

4. Cost-effectiveness

By consolidating multiple real-time systems onto fewer physical machines, virtualization can significantly reduce hardware costs, power consumption, and maintenance expenses.

Evidence: A study by Masrur et al. (2016) showed that virtualization could reduce the number of physical processors needed for real-time systems while maintaining timing guarantees, leading to potential cost savings.

5. Easier System Management and Maintenance

Virtualization simplifies system management tasks such as backup, recovery, and updates. It allows for easier migration of real-time systems between different hardware platforms.

Evidence: Research by Becker et al. (2020) demonstrated how virtualization could facilitate the deployment and management of real-time systems in industrial environments, reducing downtime and maintenance costs.

Despite these advantages, it's important to note that virtualizing real-time systems comes with its own challenges, particularly in ensuring that timing constraints are met consistently in a shared environment.

Evidence: A comprehensive survey by Aichouch et al. (2013) discussed both the benefits and challenges of real-time virtualization, highlighting areas where further research was needed to fully realize the potential of virtualized real-time systems.

In conclusion, virtualization offers significant advantages for real-time systems in terms of flexibility, resource utilization, scalability, and cost-effectiveness. However, careful consideration must be given to the specific requirements of each real-time application to ensure that virtualization can meet its timing and performance needs.

Would you like me to elaborate on any specific aspect of virtualization in real-time systems or provide more information on the challenges and potential solutions?
\end{comment}

\clearpage
\section{Objective}
